Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass V.C

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Test transplantation is effective at finding
      functional bugs. Although the cost of classifying failures was
      non-negligible, the approach revealed several non-trivial bugs
      in widely popular engines.
      \end{minipage}
    }
\end{center}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of three new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications.

@@

Table~\ref{tab:bugs} shows the list of bugs we reported. The table is
organized in two sections. The top section shows results obtained
during the exploratory phase of the study and the bottom section shows
the results obtained during the non-exploratory phase. The table shows
the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite'').

So far, ten of the bugs we reported were confirmed, two of
which were fixed. One bug report we submitted was rejected on the
basis that the offending JS file manifested an incompatibility across
engine implementations that was expected.  Note from the table that
all bug reports still waiting for confirmation are associated with the
\jsc{} engine. A closer look at the \jsc{} issue tracker showed that
their triage process is slow relative to \chakra's.\Comment{\Igor{ The bugs
  reported on \chakra{}'s bug tracker was defined as confirmed,
  however the bugs are included on a milestone for the next release
  following an internal priority.  }} As of now, we did not find any
new bug on \smonkey{} and V8; the bugs we found were duplicates and
were not reported.

@@

>>>>

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Test transplantation was effective at finding
      functional bugs. Although the cost of classifying failures was
      non-negligible, the approach revealed several non-trivial bugs
      in widely popular engines.
      \end{minipage}
    }
\end{center}

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}

@@

%% The table is
%% organized in two sections. The top section shows results obtained
%% during the exploratory phase of the study and the bottom section shows
%% the results obtained during the non-exploratory phase.

Table~\ref{tab:bugs} shows the list of bugs we reported. The table
shows the date the bug was reported (``Date''), the fuzzing tool used
(``Fuzz''), the \js\ engine affected (``Engine''), the status of the
bug report as of Aug. 24, 2018 (``Status''), the Url of the bug report
(``Url''), the severity of the bug report (``Severity''), the priority
that we assigned to the warning that revealed the bug (``Priority''),
and the test suite from the original test input (``Suite''). So far,
\Fix{ten} of the bugs we reported were confirmed, \Fix{two} of which
were fixed. Note that one bug report that we submitted was rejected on
the basis that the offending JS file manifested an incompatibility
across engine implementations that was cosidered to be acceptable. As
of now, we did not find any new bugs on \smonkey{}; the bugs we found
were duplicates and were not reported. In \veight{}, we reported two
bugs, both of which were confirmed, with one fixed.

%% Note from the table that all bug reports still waiting for
%% confirmation are associated with the \jsc{} engine. A closer look at
%% the \jsc{} issue tracker showed that their triage process is slow
%% relative to \chakra's.\Comment{\Igor{ The bugs reported on \chakra{}'s
%%     bug tracker was defined as confirmed, however the bugs are
%%     included on a milestone for the next release following an internal
%%     priority.  }}

@@

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Cross-engine differential testing was also
      effective at finding several bugs in \js\ engines. However,
      relative to test transplantation, it required substantial more
      human effort, which may play a lesser role with improved
      automation.
      \end{minipage}
    }
\end{center}

\subsection{Discussion}
